A new metric for automatic discovery of periodic patterns in time series

### 2021-03-03 paper/main.Rmd
spell check done

The quantile of a distribution with probability $p$ is defined as $Q(p)=F^{-1}(p) = inf\{x: F(x) >p\}$, $0<p< 1$ where $F(x)$ is the distribution function. There are two broad approaches to quantile estimation, viz, parametric and non-parameteric. The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data. Sample quantiles could be used for estimation in a non-parametric setup. @Hyndman1996-ty describes the difficulty in defining sample quantiles and recommends the use of median-unbiased estimator because of _*"desirable properties of a quantile estimator and can be defined independently of the underlying distribution."*_. The `stats::quantile()` function in @R-language could be used for practical implementation where type = 8 refers to the algorithm corresponding to the median-unbiased estimator. The default quantile chosen in this paper is percentiles computed for $p = {0.01, 0.02, \dots, 0.99}$, where for example, the $99^{th}$ percentile would be the value corresponding to $p=0.99$ and hence 99% of the observations would lie below that.

@@

_Generalised linear model_

@@

(3, 2), (7,9), (14, 10) being null sets and others under some other design. Generate 200 repitions of different data sets with the same design for all the pairs and compute size and power.

@@

Let $v_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$. The series $v_{i, t}$ is the linear granularity corresponding to half-hour since the interval of this data is 30 minutes. We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar. Considering $4$ linear granularities hour, day, week, month in the hierarchy table, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$. We obtain cyclic granularities namely “hour_day”, “hour_week”, “hour_month”, “day_ week”, “day_month” and “week_month”, read as “hour of the day”, etc. Further, we add cyclic granularity day-type( “wknd wday”) to capture weekend and weekday behavior. Thus, $7$ cyclic granularities are considered to be of interest. The set consisting of pairs of cyclic granularities ($C_{N_C}$) will have $7_{P_2}=42$ elements which could be analysed for detecting possible periodicities. The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2020-vo]. Table \ref{tab:tab-rank-8}  shows $14$ harmony pairs that belong to $H_{N_C}$.

>>>>

The quantile of a distribution with probability $p$ is defined as $Q(p)=F^{-1}(p) = inf\{x: F(x) >p\}$, $0<p< 1$ where $F(x)$ is the distribution function. There are two broad approaches to quantile estimation, viz, parametric and non-parametric. The benefit of using a non-parametric estimator is that there are less rigid assumptions made about the nature of the underlying distribution of the data. Sample quantiles could be used for estimation in a non-parametric setup. @Hyndman1996-ty describes the difficulty in defining sample quantiles and recommends the use of median-unbiased estimator because of _*"desirable properties of a quantile estimator and can be defined independently of the underlying distribution."*_. The `stats::quantile()` function in @R-language could be used for practical implementation where type = 8 refers to the algorithm corresponding to the median-unbiased estimator. The default quantile chosen in this paper is percentiles computed for $p = {0.01, 0.02, \dots, 0.99}$, where for example, the $99^{th}$ percentile would be the value corresponding to $p=0.99$ and hence 99% of the observations would lie below that.

@@

_Generalized linear model_

@@

(3, 2), (7,9), (14, 10) being null sets and others under some other design. Generate 200 repetitions of different data sets with the same design for all the pairs and compute size and power.

@@

Let $v_{i, t}$ denote the electricity demand for $i^{th}$ household for time period $t$. The series $v_{i, t}$ is the linear granularity corresponding to half-hour since the interval of this data is 30 minutes. We consider coarser linear granularities like hour, day, week and month from the commonly used Gregorian calendar. Considering $4$ linear granularities hour, day, week, month in the hierarchy table, the number of cyclic granularities is $N_C = (4 * 3/2) = 6$. We obtain cyclic granularities namely “hour_day”, “hour_week”, “hour_month”, “day_ week”, “day_month” and “week_month”, read as “hour of the day”, etc. Further, we add cyclic granularity day-type( “wknd wday”) to capture weekend and weekday behavior. Thus, $7$ cyclic granularities are considered to be of interest. The set consisting of pairs of cyclic granularities ($C_{N_C}$) will have $7_{P_2}=42$ elements which could be analyzed for detecting possible periodicities. The set of possible harmonies $H_{N_C}$ from $C_{N_C}$ are chosen by removing clashes using procedures described in [@Gupta2020-vo]. Table \ref{tab:tab-rank-8}  shows $14$ harmony pairs that belong to $H_{N_C}$.
